workshop

### 2022-09-13 scripts/workshop.Rmd
do transformation based pca

So we are looking for low cc distance between two sites but high bc distance
An upward trend is expected because more dissimilar sites in terms of competence probably have different composition
```{r}
bc_cc_df %>% filter(diff!=0) %>% ggplot(.,aes(x=cc_norm, y=bc_dist)) + geom_point() + geom_smooth(method = "lm")
```

@@

>>>>

So we are looking for low cc distance between two sites but high bc distance
An upward trend is expected because more dissimilar sites in terms of competence probably have different composition
```{r}
bc_cc_df %>% filter(diff!=0) %>% ggplot(.,aes(x=bc_dist, y=cc_norm)) + geom_point() + geom_smooth(method = "lm")
```

@@

```{r}
pca <- princomp(abundance_mat)

biplot(pca)

abundance_hellinger <- decostand(log1p(abundance_mat), 'hellinger')

tb_pca <- princomp(abundance_hellinger)

biplot(tb_pca)
```

```{r}
tb_pca_scores <- as.data.frame(tb_pca$scores) %>% dplyr::select(Comp.1, Comp.2) %>% rownames_to_column(., var = "siteID")

tb_pca_scores_summ <- left_join(comm_summ, tb_pca_scores, by = "siteID")

tb_pca_scores_summ$Month <- factor(tb_pca_scores_summ$Month, levels = c("Feb", "Mar", "Apr", "May", "Jun", "Jul"))

tb_pca_scores_summ %<>% mutate(pc1Rank=dense_rank(Comp.1))

tb_pca_scores_summ %>% ggplot(.,aes(x=pc1Rank, y=cc)) + geom_point()

tb_pca_scores_summ %>% ggplot(.,aes(x=Comp.1, y=cc)) + geom_point() + geom_smooth(method = "loess")

### Let's try to explain the residuals

The residuals from the cc_norm ~ bc_dist represent when the community competence is more or less similar than expected given the similarity of the community. If community composition is not explaining similarity in community competence then this must be due to the two communities having
